---
title: "Fish and Surfers"
author: "Villaseñor-Derbez, J.C."
date: "5 minutes before deadline"
output: 
  pdf_document: 
    fig_caption: yes
    fig_height: 2
    fig_width: 6
bibliography: references.bib
# csl: ieee.csl
---

# Abstract

We looked at fish and surfers, and draw wild, unsupported conclusions.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction

There are many fish in California. They have widely been studied [@love_2011].

# Methods

We counted fish and surfers, and placed them into tidy dataset [@wickham_2014]

# Results

```{r load packages}
#install.packages("tidyverse")

suppressPackageStartupMessages({
  library(stargazer)
  library(knitr)
  library(kableExtra)
  library(tidyverse)
})
```

```{r load data}
taxa_table <- read.csv("taxa_table.csv")
```

Our extensive survey identified a total of `r sum(taxa_table$Surfers)` Surfers and `r sum(taxa_table$Count)`, with `r length(unique(taxa_table$Species))` species, distributed along `r length(unique(taxa_table$Genus))` Genus and `r length(unique(taxa_table$Family))` Families. 

We tested the relationship between fish abundance and surfers (Fig. \ref{fig:fishplot}) with a linear regression with the form:

$$Fish = \beta_0 + beta_1Surfers$$

```{r plot data, fig.cap="\\label{fig:fishplot}Relationship between fish abundance and surfers"}
ggplot(taxa_table, aes(x = Surfers, y = Count)) +
  geom_point(aes(color = Family), size = 2) +
  theme_bw() +
  geom_smooth(method = "lm", color = "black", linetype = "dashed", alpha = 0.2)
```

\clearpage

```{r, results = "asis"}
model <- lm(Count ~ Surfers, taxa_table)
stargazer::stargazer(model, header = F, single.row = T, omit.stat = "adj.rsq", title = "My results table!")
```

# Conclusions

Surfers scare fish.

# References





